Jug: Software for Reproducible Computation

### 2013-05-16 paper.tex
TXT Update download count.
I wonder if the previous very low value was a typo.

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
through June~2012 and has been downloaded over 13,000~times (some of these
downloads may, of course, represent upgrades, and users which downloaded it
from some other source will not be counted).

>>>>

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
through May~2013 and has been downloaded over 43,000~times (some of these
downloads may, of course, represent upgrades, and users which downloaded it
from some other source will not be counted).
